Do Alternate Wetting and Drying Irrigation Technology and Nitrogen Rates Affect Rice Sheath Blight?

### 2020-07-06 analysis/paper/paper.Rmd
Fix colnames so that paper knits

p2 <- ggplot(RAW_data,
             aes(x = DAI,
                 y = PERCENT_TIL_ShB)) +
  geom_text(
    data = p2_anot,
    mapping = aes(x = x,
                  y = y,
                  label = label)) +
  stat_summary(fun.y = "mean",
               geom = "line",
               aes(group = WMGT,
                   linetype = WMGT)) +
  stat_summary(fun.y = "mean",
               geom = "point",
               aes(group = WMGT,
                   shape = WMGT)) +
  scale_y_continuous(name = "Tiller Severity (%)") +
  xlab("Days After Inoculation") +
  facet_grid(. ~ YEAR,
             scales = "free_x") +
  theme_classic(base_size = 8) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black"),
        legend.position = "none",
        axis.title.x = element_blank(),
        strip.background = element_blank(),
        strip.text.x = element_blank())

@@

p3 <- ggplot(RAW_data,
             aes(x = DAI,
                 y = PERCENT_LEAF_ShB)) +
  geom_text(
    data = p3_anot,
    mapping = aes(x = x,
                  y = y,
                  label = label)) +
  stat_summary(fun.y = "mean",
               geom = "line",
               aes(group = WMGT,
                   linetype = WMGT)) +
  stat_summary(fun.y = "mean",
               geom = "point",
               aes(group = WMGT,
                   shape = WMGT)) +
  scale_y_continuous(name = "Leaf Severity (%)") +
  xlab("Days After Inoculation") +
  facet_grid(. ~ YEAR,
             scales = "free_x") +
  theme_classic(base_size = 8) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black"),
        legend.position = "none",
        strip.background = element_blank(),
        strip.text.x = element_blank())

@@

p5 <- ggplot(RAW_data,
             aes(x = DAI,
                 y = PERCENT_TIL_ShB)) +
  geom_text(
    data = p5_anot,
    mapping = aes(x = x,
                  y = y,
                  label = label)) +
  stat_summary(fun.y = "mean",
               geom = "line",
               aes(group = NRTE,
                   linetype = NRTE)) +
  stat_summary(fun.y = "mean",
               geom = "point",
               aes(group = NRTE,
                   shape = NRTE)) +
  scale_y_continuous(name = "Tiller Severity (%)") +
  xlab("Days After Inoculation") +
  facet_grid(. ~ YEAR,
             scales = "free_x") +
  theme_classic(base_size = 8) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black"),
        legend.position = "none",
        axis.title.x = element_blank(),
        strip.background = element_blank(),
        strip.text.x = element_blank())

@@

p6 <- ggplot(RAW_data,
             aes(x = DAI,
                 y = PERCENT_LEAF_ShB)) +
  geom_text(
    data = p6_anot,
    mapping = aes(x = x,
                  y = y,
                  label = label)) +
  stat_summary(fun.y = "mean",
               geom = "line",
               aes(group = NRTE,
                   linetype = NRTE)) +
  stat_summary(fun.y = "mean",
               geom = "point",
               aes(group = NRTE,
                   shape = NRTE)) +
  scale_y_continuous(name = "Leaf Severity (%)") +
  xlab("Days After Inoculation") +
  facet_grid(. ~ YEAR,
             scales = "free_x") +
  theme_classic(base_size = 8) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black"),
        legend.position = "none",
        strip.background = element_blank(),
        strip.text.x = element_blank())

>>>>

p2 <- ggplot(RAW_data,
             aes(x = DAI,
                 y = TIL_ShB)) +
  geom_text(
    data = p2_anot,
    mapping = aes(x = x,
                  y = y,
                  label = label)) +
  stat_summary(fun.y = "mean",
               geom = "line",
               aes(group = WMGT,
                   linetype = WMGT)) +
  stat_summary(fun.y = "mean",
               geom = "point",
               aes(group = WMGT,
                   shape = WMGT)) +
  scale_y_continuous(name = "Tiller Severity (0 - 5 scale)") +
  xlab("Days After Inoculation") +
  facet_grid(. ~ YEAR,
             scales = "free_x") +
  theme_classic(base_size = 8) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black"),
        legend.position = "none",
        axis.title.x = element_blank(),
        strip.background = element_blank(),
        strip.text.x = element_blank())

@@

p3 <- ggplot(RAW_data,
             aes(x = DAI,
                 y = LEAF_ShB)) +
  geom_text(
    data = p3_anot,
    mapping = aes(x = x,
                  y = y,
                  label = label)) +
  stat_summary(fun.y = "mean",
               geom = "line",
               aes(group = WMGT,
                   linetype = WMGT)) +
  stat_summary(fun.y = "mean",
               geom = "point",
               aes(group = WMGT,
                   shape = WMGT)) +
  scale_y_continuous(name = "Leaf Severity (0 - 5 scale)") +
  xlab("Days After Inoculation") +
  facet_grid(. ~ YEAR,
             scales = "free_x") +
  theme_classic(base_size = 8) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black"),
        legend.position = "none",
        strip.background = element_blank(),
        strip.text.x = element_blank())

@@

p5 <- ggplot(RAW_data,
             aes(x = DAI,
                 y = TIL_ShB)) +
  geom_text(
    data = p5_anot,
    mapping = aes(x = x,
                  y = y,
                  label = label)) +
  stat_summary(fun.y = "mean",
               geom = "line",
               aes(group = NRTE,
                   linetype = NRTE)) +
  stat_summary(fun.y = "mean",
               geom = "point",
               aes(group = NRTE,
                   shape = NRTE)) +
  scale_y_continuous(name = "Tiller Severity 0 - 5 scale)") +
  xlab("Days After Inoculation") +
  facet_grid(. ~ YEAR,
             scales = "free_x") +
  theme_classic(base_size = 8) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black"),
        legend.position = "none",
        axis.title.x = element_blank(),
        strip.background = element_blank(),
        strip.text.x = element_blank())

@@

p6 <- ggplot(RAW_data,
             aes(x = DAI,
                 y = LEAF_ShB)) +
  geom_text(
    data = p6_anot,
    mapping = aes(x = x,
                  y = y,
                  label = label)) +
  stat_summary(fun.y = "mean",
               geom = "line",
               aes(group = NRTE,
                   linetype = NRTE)) +
  stat_summary(fun.y = "mean",
               geom = "point",
               aes(group = NRTE,
                   shape = NRTE)) +
  scale_y_continuous(name = "Leaf Severity (0 - 5 scale)") +
  xlab("Days After Inoculation") +
  facet_grid(. ~ YEAR,
             scales = "free_x") +
  theme_classic(base_size = 8) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black"),
        legend.position = "none",
        strip.background = element_blank(),
        strip.text.x = element_blank())
